### 2023-03-14 chapter0/chapter0.tex
Added paragraph about comparative genomics to aims

>>>>

Though modern genetic engineering techniques enable the direct manipulation of DNA sequences in living systems, gene editing remains a lengthy and work-intensive process in fruit flies. Therefore, experimentally testing the vast number of sequences needed to fully map the relationship between distributed features and function in IDRs is infeasible. The comparative genomics approach instead leverages the work done by nature to identify evolutionarily conserved features and generate specific hypotheses to guide experiments~\cite{Hardison2003}. As life is constantly exploring the space of allowed proteins through evolutionary change, features which are unimportant for a protein's function, or at a larger scale, an organism's survival offer no benefit for their maintenance and are therefore gradually degraded and lost. Thus, conservation in related sequences is powerful signal of function.
